Hope

### 2024-05-28 paper/IEEES/paper.tex
Added some more text

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
  Despite the recent growth of zero-knowledge succinct argument 
  of knowledge (ZkSNARK) in cryptocurrencies, 
  sigma protocol remains a popular choice in electronic voting to maintain privacy 
  and verifiability of elections and still used in prominent e-voting systems such as 
  Helios, Belenois, SwissPost, etc. However, 
  the existing implementations of sigma protocol have two 
  shortcomings: (i) the same code is written twice, once for the front-end (JavaScript)
  and once for the back-end (Python/OCaml/Java), which is time-consuming but more importantly error-prone, 
  and (ii) none of these implementations offer any security guarantees. 
  In this paper, we present a certified implementation of sigma protocol in the Coq proof assistant and
  prove our implementation is (special) sound, complete, and 
  (honest verifier) zero-knowledge. Finally, 
  we compile our Coq formalisation to WebAssembly and Rust, and 
  thereby solve the problem of writing the same code twice. 
  We demonstrate the applicability of our
  formalisation by encoding the sigma protcol implemented in 
  Helios, Belenois, and SwissPost voting systems. 
  Our long terms goal is to provide a verified cryptographic library that can be 
  readily used in privacy-preserving voting systems.
\end{abstract}

@@

\section{Introduction}
Electronic voting offers convenience and efficiency in electoral processes, 
potentially improving accessibility for disabled voters, increasing participation 
among overseas voters, and lowering the costs associated with conducting elections.
Privacy and verifiability are two crucial elements that a voting system 
must ensure to adhere with the principles of a free-and-fair election.  
In a paper-ballot election, we achieve privacy by ensuring that 
no identifying information is present on a ballot that links the ballot to a particular voter
and verifiability by means of scrutineers closely observing various electoral 
processes, including counting of ballots. In order to have a similar effect in electronic 
voting, encryption is employed to safeguard the privacy 
of voter choices, while public verifiable evidences (zero-knowledge proof)
allow voters and independent observers to verify the integrity 
of the voting process. However, a cryptographic techniques, no matter how 
advance,  are useless if their software implementation contains bugs. 
In fact, due to a major cryptographic flaw that
could let someone change votes cast using Switzerland's online 
voting software without being detected  \cite{9152765}, the Swiss Federal Chancellery suspended electronic voting in 
2019. It only resumed in 2023 after getting feedbacks from academic 
community \cite{swiss_evoting_chronik} about various component used in 
the electronic voting software. However, it is not an isolated  
instance where bugs have been found in a voting software, e.g., 
Voatz \cite{255334} (used in West Virginia, USA election),
Democracy Live Online Voting System \cite{263858} 
(used in Delaware, West Virginia, and New Jersey, USA election), 
Moscow Internet Voting System \cite{10.1007/978-3-030-51280-4_3}
(used in Russia election), and iVote System \cite{10.1007/978-3-319-22270-7_3, 10.1145/3014812.3014837} 
(used in New South Wales, Australia election), etc. 
These unfortunate situations can largely be attributed to two factors: 
(i) closed source code (proprietary artifacts) because most of these bugs were 
discovered by researchers who inspected the code after they were made public, and 
(ii) software testing which is inadequate to rule out all the bugs 
from a software. To eliminate potential bugs from software, formal verification has 
emerged as a promising solution. In recent years, it has been increasingly 
adopted in real-world software applications \cite{10.1145/1111037.1111042}, 
including cryptography \cite{8835346,10.1145/3133956.3134043,190894,10.1145/2701415,
10.1145/2660267.2660370,10.1145/3319535.3363211}.

\textbf{Our contributions:}
In this paper, we present a certified implementation of the Sigma protocol --an efficient 
type of zero-knowledge proof-- and its Parallel, And, Eq, Or, and Neq compositions in 
the Coq proof assistant. We have formalised and analysed the interactive version of 
the Sigma protocol, but in practice it is not convenient due to the required interaction. 
Therefore, all Sigma protocol implementations use the Fiat-Shamir 
transformation \cite{10.5555/36664.36676} to make them non-interactive. This involves 
using a hash function to replace the randomness of the public-coin verifier, though 
some care is required \cite{10.1007/978-3-642-34961-4_38}.
To make our formalisation self-contained and independent of external libraries, we have 
encoded SHA-256 in Coq and proven its usual correctness properties. Additionally, we 
have implemented efficient prime field arithmetic procedures and the Schnorr group to 
ensure our library is concrete and executable. Finally, we extract WebAssembly and 
Rust code from our certified implementation, one of the novelties of our 
formalisation.

@@

In the Schnorr protocol, $g, h, c$ are group elements from underlying group, while 
$u, e, t$ are scalar values from underlying prime field. In practice, 
both the group elements and the fields elements are some large prime numbers,
albeit the operations differ. For most of the languages it does not matter, 
but also a potential source of bugs (cite thomas work here). However, 
we need to flesh down all the details while encoding it Coq. One possibility is 
to encode the Coq functions to work with concrete numbers but this leads to 
cumbersome proofs because of dealing with concrete numbers. In our formalisation, 
we decided to abstract the underlying group as an abstract type $G$, endowed with 
usual group operation, and the underlying field as an abstract type $F$, endowed with 
filed operation. Finally, we abstract these two types in an vector space. This 
makes our formalisation generic that can be instantiated with 
any kind of group and field as long as it follows the axioms of 
vector space. For example, in our formalisation we have developed 
efficient algorithm for Schnorr group but our formalisation can 
later be also instantiated with elliptic curve group. However, 
one of the major benefit of this abstraction is easiness of proofs 
which can be easily automated.

We model the Schnorr protocol in Coq as follows:

\begin{lstlisting}[language=Coq]
  Definition schnorr_protocol (x : F) (g : G) (u c : F) : 
    @sigma_proto 1 1 1 :=  ([g^u]; [c]; [u + c * x]).
\end{lstlisting}

 where $F$ is the underlying field, $G$ is the underlying group,
 $+ : F \rightarrow F \rightarrow F$ is field addition,
 $* : F \rightarrow F \rightarrow F$ is field multiplication, and
 $: G \rightarrow F \rightarrow G$ scalor multiplication. 
 We emphasise that we work in abstract setting of \textbf{vector space} to 
 make the implementation as general as possible. Recall that a vector space consists of a set of 
 vectors, denoted by \(V\), a field \(F\) (elements of F are called scalars), and 
 two operations: vector addition and scalar multiplication.

\begin{itemize}
    \item \textit{Vector addition}: for any vectors \(\mathbf{v}, \mathbf{w} \in V\), their sum, denoted by \(\mathbf{v} + \mathbf{w}\), is also in \(V\).
    \item \textit{Scalar multiplication}: for any vector \(\mathbf{v} \in V\) and any scalar \(c \in F\), their product, denoted by \(c\mathbf{v}\), is also in \(V\).
\end{itemize}

These operations must satisfy the following properties for all vectors \(\mathbf{u}, \mathbf{v}, \mathbf{w} \in V\) and all scalars \(c, d \in F\):
(i) \textbf{Closure under addition:} \(\mathbf{u} + \mathbf{v} \in V\), (ii) \textbf{Commutativity of addition:} \(\mathbf{u} + \mathbf{v} = \mathbf{v} + \mathbf{u}\), 
(iii)  \textbf{Associativity of addition:} \((\mathbf{u} + \mathbf{v}) + \mathbf{w} = \mathbf{u} + (\mathbf{v} + \mathbf{w})\), 
(iv) \textbf{Existence of zero vector:} There exists a vector \(\mathbf{0} \in V\) such that \(\mathbf{v} + \mathbf{0} = \mathbf{v}\) for all \(\mathbf{v} \in V\), 
(v) \textbf{Existence of additive inverse:} For each vector \(\mathbf{v} \in V\), there exists a vector \(-\mathbf{v} \in V\) such that \(\mathbf{v} + (-\mathbf{v}) = \mathbf{0}\),
(vi) \textbf{Closure under scalar multiplication:} \(c\mathbf{v} \in V\), 
(vii) \textbf{Distributive properties:} \(c(\mathbf{u} + \mathbf{v}) = c\mathbf{u} + c\mathbf{v}\) and \((c + d)\mathbf{v} = c\mathbf{v} + d\mathbf{v}\), 
and (viii) \textbf{Compatibility with field multiplication:} \(c(d\mathbf{v}) = (cd)\mathbf{v}\) and \(1\mathbf{v} = \mathbf{v}\), where \(1\) denotes the multiplicative identity in \(F\).
In our setting we instantiate the set of vectors with group $G$ and field with $F$. Moreover, our notation for scalar multiplication 
is because it represents, when instantiated concretely, exponentiation function. Finally, 
we define two more functions

\begin{lstlisting}[language=Coq]
  (* Fake transcript (without the witness x) *)
  Definition schnorr_simulator (g h : G) (u c : F) : 
  @sigma_proto 1 1 1 := ([gop (g^u) (h^(opp c))]; [c]; [u]).

  (* 
    This function checks if a conversation (a; c; r) 
    is accepting or not. It checks if g^r = a * h^c
  *)
  Definition accepting_conversation 
    (g h : G) (v : @sigma_proto 1 1 1) : bool :=
    match v with
    | (a; c; r) =>  
      match Gdec (g^(hd r)) (gop (hd a) (h^(hd c))) with 
      | left _ => true
      | right _ => false 
      end
    end.

  (* Distribution that involves the secret x *)
  Definition schnorr_distribution  (lf : list F) 
    (Hlfn : lf <> List.nil) (x : F) (g : G) (c : F) : 
    dist sigma_proto :=
    (* draw u from a random distribution *)
    u <- (uniform_with_replacement lf Hlfn) ;;
    Ret (schnorr_protocol x g u c).

  (* without secret x *)
  Definition simulator_distribution (lf : list F) 
    (Hlfn : lf <> List.nil) (g h : G) (c : F) : 
    dist sigma_proto :=
    (* draw u from a random distribution *)
    u <- (uniform_with_replacement lf Hlfn) ;;
    Ret (schnorr_simulator g h u c).
  \end{lstlisting}

  Finally we establish the completeness, special soundness, 
  and special honest-verifier zero-knowledge proof.

@@

  Lemma simulator_completeness : 
      forall (r c : F) (a : t G 1) (c r : t F 1),
      (a; c; r) = (schnorr_simulator g h r c) ->
      accepting_conversation g h (a; c; r) = true.
    Proof using -(x R). (* proof terms omitted *) Qed.

  Lemma special_soundness: 
    forall (a : G) (ca ra cb rb : F), ca <> cb ->
    accepting_conversation g h ([a]; [ca]; [ra]) = true ->  
    accepting_conversation g h ([a]; [cb]; [rb]) = true ->
    (* then we can find a witness y such that g^y = h *)
    exists y : F, g^y = h /\ y = ((ra - rb) * inv (ca - cb)).
  Proof using -(x R). (* proof terms omitted *) Qed.

  (* it's identical, i.e., information theoretic zero-knowledge proof *)
  (* Under the hood, it is modelled as a list and looks like:
      [((a; c; r), prob); ((a; c; r), prob) ......].
    We map accepting_conversation to crunch the first pair, 
    (a, c, r), and produce boolean a value (true), 
    and then we show that these two distribution are 
    identical 
  *)
  Lemma special_honest_verifier_zkp : 
    forall (lf : list F) (Hlfn : lf <> List.nil) (c : F), 
    List.map (fun '(a, p) => (accepting_conversation g h a, p))
      (@schnorr_distribution lf Hlfn x g c) = 
    List.map (fun '(a, p) => (accepting_conversation g h a, p))
      (@simulator_distribution lf Hlfn g h c).
  Proof. (* proof terms omitted *) Qed.

@@

In our library, we have encoded Parallel composition, 
AND composition, OR composition, EQ composition, and 
NEQ composition. Below we explain the OR composition
beause it is more involved than the rest.

  However, we would like 
  to emphasise that we worked in a vector-space, rather 
  than concrete numbers. Working in (abstract) vector-space makes our system 
  amenable to be instantiated by any group and field 
  (Elliptic curve vs Concrete Nubmers). \textbf{Currently, 
  our library comes with concrete nubmers but it can easily be 
  instantiated with Elliptic curve cryptography}

  \textbf{Coq code of Schnorr goes here}

  The reader can see that we have used vector space. Now 
  we establish completeness, (special) soundness, and zero-knowledge 
  proof of knowledge (ZkPOK).

  \textbf{Coq code soundness, completeness, zkp goes here}

  The proof of completeness and soundness are fairly straightforward but 
  zero-knowledge proof of knowledge requires probabilistic reasoning.

  \textbf{Coq code goes here}

  In our library, we have encoded Parallel composition, 
  And composition, Or composition, EQ composition, and 
  NEQ composition. Below we explain the OR composition
  beause it is more involved than the rest.

  \textbf{OR composition and Coq code}

  \subsection{Uniform Distribution}
  To reason about special honest-verifier zero-knowledge proof 
  intuitively, we need a model of uniform distribution. 
  we encode distribution a list of tuples where the 
  second element of tuple basically is probability of first element 
  in the tuple. Moreover, we define equality on distribution by 
  stating that two distributions are equal if they are permutation 
  of each other.

@@

  Definition dist_equiv {A : Type} : relation (dist A) := 
  fun xs ys => Permutation xs ys.

  (* Probability Monad *)
  Definition Ret {A : Type} (x : A) : dist A := [(x, one)].

@@

    (* Uniform distribution u*)
    Definition uniform_with_replacement {A : Type} : 
      forall (l : list A), l <> [] -> dist A.
    Proof.
      intros ? H.
      remember (Pos.of_nat (List.length l)) as len.
      exact (List.map 
        (fun x => (x, mk_prob 1 len)) l).
    Defined.

    Fixpoint repeat_dist_ntimes_vector {A : Type} 
      (d : dist A) 
      (n : nat) : dist (Vector.t A n) := 
    match n with 
    | 0 => Ret (@Vector.nil A)
    | S n' => 
      Bind d (fun u => 
        Bind (repeat_dist_ntimes_vector d n')
        (fun v => Ret (Vector.cons _ u _ v)))
    end.

    Lemma uniform_probability_multidraw_prob {A : Type} :
      forall n lf (a : Vector.t A n) b (Hlf : lf <> []), 
      In (a, b) (repeat_dist_ntimes_vector 
        (uniform_with_replacement lf Hlf) n) ->
      b = mk_prob 1 (Pos.of_nat 
      (Nat.pow (List.length lf) n)).
  \end{lstlisting}

  We use the $uniform\_probability\_multidraw\_prop$ theorem 
  for special honest-verifier zero-knowledge proof.

@@

(* schnorr distribution *)
    Definition generalised_or_schnorr_distribution  
      {n m : nat} (lf : list F) (Hlfn : lf <> List.nil) 
      (x : F) (gs hs : Vector.t G (m + (1 + n))) (c : F) : 
      dist (@sigma_proto (m + (1 + n)) 
        (1 + (m + (1 + n))) (m + (1 + n))) :=
      (* draw ((m + (1 + n)) + (m + n)) random elements *)
      usrs <- repeat_dist_ntimes_vector 
        (uniform_with_replacement lf Hlfn) ((m + (1 + n)) + (m + n)) ;;
      Ret (construct_or_conversations_schnorr x gs hs usrs c).

    (* simulator distribution *)
    Definition generalised_or_simulator_distribution  
      {n m : nat} (lf : list F) (Hlfn : lf <> List.nil) 
      (gs hs : Vector.t G (m + (1 + n))) (c : F) : 
      dist (@sigma_proto (m + (1 + n)) 
        (1 + (m + (1 + n))) (m + (1 + n))) :=
      (* draw ((m + (1 + n)) + (m + n)) random elements *)
      usrs <- repeat_dist_ntimes_vector 
        (uniform_with_replacement lf Hlfn) ((m + (1 + n)) + (m + n)) ;;
      Ret (construct_or_conversations_simulator gs hs usrs c).

@@

  \subsection{Efficient Modular Arithmetic}
  In order to call the functions from our formalisation, 
  a user need to instantiate

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
  Despite the recent growth of zero-knowledge succinct argument 
  of knowledge (ZkSNARK) in cryptocurrencies, 
  sigma protocol remains a popular choice in electronic voting to maintain privacy 
  and verifiability of elections and still used in prominent e-voting systems such as 
  Helios, Belenois, SwissPost, etc. However, 
  the existing implementations of sigma protocol have two 
  shortcomings: (i) the same code is written twice, once for the front-end (JavaScript)
  and once for the back-end (Python/OCaml/Java), which is time-consuming but more importantly error-prone, 
  and (ii) none of these implementations offer any security guarantees.

  In this paper, we present a certified implementation of sigma protocol in the Coq proof assistant and
  prove our implementation is (special) sound, complete, and 
  (honest verifier) zero-knowledge. Moreover, 
  we compile our Coq formalisation to WebAssembly and Rust; 
  thereby solve the problem of writing the same code twice. 
  We demonstrate the applicability of our
  formalisation by encoding the sigma protcol implemented in 
  Helios, Belenois, and SwissPost voting systems. 
  Our long terms goal is to provide a verified cryptographic library that can be 
  readily used in privacy-preserving voting systems.
\end{abstract}

@@

\section{Introduction}
Electronic voting offers convenience and efficiency in electoral processes, potentially improving 
accessibility for disabled voters, increasing participation among overseas voters, and lowering 
the costs associated with conducting elections. Moreover,
they can streamline the voting process, reduce administrative burdens, and enable 
faster tallying of results. However, the transition to electronic voting also brings significant 
challenges, particularly in ensuring the privacy and verifiability of the voting process. Therefore, 
privacy and verifiability are two crucial elements that a voting system must ensure to adhere with 
the principles of a free-and-fair election. In a paper-ballot election, privacy is maintained by 
ensuring that no identifying information is present on a ballot that links it to a particular voter, 
and verifiability is achieved through scrutineers closely observing various electoral processes, 
including the counting of ballots. In order to have a similar effect in electronic voting, encryption 
is employed to safeguard the privacy of voter choices, while publicly verifiable evidence 
(such as zero-knowledge proofs) allows voters and independent observers to verify the integrity of 
the voting process. However, no matter how advanced the cryptographic techniques, they are useless 
if their software implementation contains bugs.
In fact, due to a major cryptographic flaw that
could let someone change votes cast using Switzerland's online 
voting software without being detected  \cite{9152765}, the Swiss Federal Chancellery suspended electronic voting in 
2019. It only resumed in 2023 after getting feedbacks from academic 
community \cite{swiss_evoting_chronik} about various component used in 
the electronic voting software. However, it is not an isolated  
instance where bugs have been found in a voting software, e.g., 
Voatz \cite{255334} (used in West Virginia, USA election),
Democracy Live Online Voting System \cite{263858} 
(used in Delaware, West Virginia, and New Jersey, USA election), 
Moscow Internet Voting System \cite{10.1007/978-3-030-51280-4_3}
(used in Russia election), and iVote System \cite{10.1007/978-3-319-22270-7_3, 10.1145/3014812.3014837} 
(used in New South Wales, Australia election), etc. 
These unfortunate situations can largely be attributed to two factors: 
(i) closed source code (proprietary artifacts) because most of these bugs were 
discovered by researchers who inspected the code after they were made public, and 
(ii) software testing which is inadequate to rule out all the bugs 
from a software. Therefore, to avoid the situations like this, 
an electronic voting system must adhere to \textit{software independence}\cite{rivest2008notion}:
\begin{quote}
  A voting system is software-independent if an
  (undetected) change or error in its software cannot
  cause an undetectable change or error in an
  election outcome. 
\end{quote}
\noindent
Therefore, many electronic voting systems follow the principals 
of \textit{end-to-end verifiability}. End-to-end verifiability is 
defined as: 
\begin{itemize}
  \item Cast-as-intended: voters get proof that the electronic ballot accurately reflects their choices.
  \item Collected-as-cast: the election authority provides proof that the electronic ballots are received without tampering.
  \item Counted-as-collected: the election authority provides proof that the results are based on correctly counting all received ballots.
\end{itemize}

\noindent 
Finally, voters or scrutineers inspect these proofs and accept or reject the election results based on 
the verification of these proofs. In practice, this means that during the execution of an election, 
electronic voting software generates data, and voters and scrutineers verify the conformity of 
this data using independently written computer programs. The rationale is that if there is 
any discrepancy in the electronic voting system, at least one scrutineer or voter would detect it.
It is important to note that end-to-end verifiability is a valuable feature because it 
allows for the verification of the election results by checking the proofs of correctness 
only after the election has concluded. This ensures that the election process was conducted 
properly and that the results are accurate, but it is applied after the voting has taken place.
The question arises: can we use it before an election?
The answer is yes; we use a formal language to express end-to-end verifiability, or parts of 
it and develop various components of electronic voting 
software in this formal language. This process is called as formal verification and it ensures 
that the software always produces valid proofs, 
which are consistently accepted by voters and scrutineers. In other words, formal verification
can be employed to develop reliable electronic voting software.
In fact, formal verification has emerged as a promising solution 
to eliminate potential bugs from software, and in recent years it has been increasingly 
adopted in real-world software applications \cite{10.1145/1111037.1111042}, 
including cryptography \cite{8835346,10.1145/3133956.3134043,190894,10.1145/2701415,
10.1145/2660267.2660370,10.1145/3319535.3363211}.

In this paper, we present a certified implementation of the Sigma protocol --an efficient 
type of zero-knowledge proof-- and its Parallel, And, Eq, Or, and Neq compositions in 
the formal language of Coq proof assistant. Given that the formal language of Coq 
is constructive, we get an implementation that can be executed on a computer.

We have formalised and analysed the interactive version of 
the Sigma protocol, but in practice it is not convenient due to the required interaction. 
Therefore, all Sigma protocol implementations use the Fiat-Shamir 
transformation \cite{10.5555/36664.36676} to make them non-interactive. This involves 
using a hash function to replace the randomness of the public-coin verifier, though 
some care is required \cite{10.1007/978-3-642-34961-4_38}.
To make our formalisation self-contained and independent of external libraries, we have 
encoded SHA-256 in Coq and proven its usual correctness properties. Additionally, we 
have implemented efficient prime field arithmetic procedures and the Schnorr group to 
ensure our library is concrete and executable. Finally, we extract WebAssembly and 
Rust code from our certified implementation, one of the novelties of our 
formalisation.

@@

In the Schnorr protocol, $g, h, c$ are group elements from underlying group, while 
$u, e, t$ are scalar values from underlying prime field. In practice, 
both the group elements and the fields elements are some large prime numbers,
albeit the operations differ. For most of the languages it does not matter, 
but also a potential source of bugs (cite thomas work here). However, 
we need to flesh down all the details while encoding it Coq. One possibility is 
to encode the Coq functions to work with concrete numbers but this leads to 
cumbersome proofs because of dealing with concrete numbers. In our formalisation, 
we decided to abstract the underlying group as an abstract type $G$, endowed with 
usual group operation, and the underlying field as an abstract type $F$, endowed with 
filed operation. Finally, we abstract these two types in an vector space. This 
makes our formalisation generic that can be instantiated with 
any kind of group and field as long as it follows the axioms of 
vector space. For example, in our formalisation we have developed 
efficient algorithm for Schnorr group but our formalisation can 
later be also instantiated with elliptic curve group. However, 
one of the major benefit of this abstraction is easiness of proofs 
which can be easily automated. Therefore, we model the Schnorr 
protoco, the simulator, and the verification equation in Coq as follows:

\begin{lstlisting}[language=Coq]
(*Real transcript (involves secret x)*)
Definition schnorr_protocol (x : F) (g : G) (u c : F) : 
 sigma_proto :=  ([g^u]; [c]; [u + c * x]).

(*Fake transcript (without the witness x)*)
Definition schnorr_simulator (g h : G) (u c : F) :
  sigma_proto := ([gop (g^u) (h^(opp c))]; [c]; [u]).

(*This function checks if a transcript 
(a; c; r) is accepting or not. It checks
if g^r = a * h^c*)
Definition accepting_conversation 
  (g h : G) (v : sigma_proto) : bool :=
  match v with
  | (a; c; r) =>  
    match Gdec (g^r) (gop a (h^c)) with 
    | left _ => true
    | right _ => false 
    end
  end.
\end{lstlisting}

\noindent
 where $F$ is the underlying field, $G$ is the underlying group,
 $+ : F \rightarrow F \rightarrow F$ is field addition,
 $* : F \rightarrow F \rightarrow F$ is field multiplication, and
 $\mbox{\textasciicircum}: G \rightarrow F \rightarrow G$ scalar multiplication of vector space.  
 Recall that a vector space consists of a set of 
 vectors, denoted by \(V\), a field \(F\) (elements of F are called scalars), and 
 two operations: vector addition and scalar multiplication.
\begin{itemize}
    \item \textit{Vector addition}: for any vectors \(\mathbf{v}, \mathbf{w} \in V\), their sum, denoted by \(\mathbf{v} + \mathbf{w}\), is also in \(V\).
    \item \textit{Scalar multiplication}: for any vector \(\mathbf{v} \in V\) and any scalar \(c \in F\), their product, denoted by \(c\mathbf{v}\), is also in \(V\).
\end{itemize}

These operations must satisfy the following properties for all vectors \(\mathbf{u}, \mathbf{v}, \mathbf{w} \in V\) and all scalars \(c, d \in F\):
(i) \textbf{closure under addition:} \(\mathbf{u} + \mathbf{v} \in V\), (ii) \textbf{commutativity of addition:} \(\mathbf{u} + \mathbf{v} = \mathbf{v} + \mathbf{u}\), 
(iii)  \textbf{associativity of addition:} \((\mathbf{u} + \mathbf{v}) + \mathbf{w} = \mathbf{u} + (\mathbf{v} + \mathbf{w})\), 
(iv) \textbf{existence of zero vector:} there exists a vector \(\mathbf{0} \in V\) such that \(\mathbf{v} + \mathbf{0} = \mathbf{v}\) for all \(\mathbf{v} \in V\), 
(v) \textbf{existence of additive inverse:} for each vector \(\mathbf{v} \in V\), there exists a vector \(-\mathbf{v} \in V\) such that \(\mathbf{v} + (-\mathbf{v}) = \mathbf{0}\),
(vi) \textbf{closure under scalar multiplication:} \(c\mathbf{v} \in V\), 
(vii) \textbf{cistributive properties:} \(c(\mathbf{u} + \mathbf{v}) = c\mathbf{u} + c\mathbf{v}\) and \((c + d)\mathbf{v} = c\mathbf{v} + d\mathbf{v}\), 
and (viii) \textbf{compatibility with field multiplication:} \(c(d\mathbf{v}) = (cd)\mathbf{v}\) and \(1\mathbf{v} = \mathbf{v}\), where \(1\) denotes the multiplicative identity in \(F\).
In our setting we instantiate the set of vectors with $G$ and field with $F$. 
Moreover, our notation for scalar multiplication is $\mbox{\textasciicircum}$ because it represents, 
when instantiated concretely, exponentiation function but it is purely for notational convenience.

We prove the completeness and special soundness property of the Schnorr protocol, 
as shown in the figure .... We however cannot prove the special honest-verifier 
zero-knowledge property yet because it requires reasoning about probability that 
we discuss in the next section.

@@

Lemma simulator_completeness : 
forall (r c : F) (a : t G 1) (c r : t F 1),
(a; c; r) = (schnorr_simulator g h r c) ->
accepting_conversation g h (a; c; r) = true.
Proof using -(x R). (* terms omitted *) Qed.

Lemma special_soundness: 
forall (a : G) (ca ra cb rb : F), ca <> cb ->
accepting_conversation g h ([a]; [ca]; [ra]) = true ->  
accepting_conversation g h ([a]; [cb]; [rb]) = true ->
exists y : F, g^y = h /\ y = ((ra - rb) * inv (ca - cb)).
Proof using -(x R). (* proof terms omitted *) Qed.

@@

  \subsection{Uniform Distribution}
  To reason about special honest-verifier zero-knowledge proof 
  intuitively, we need a model of uniform distribution. 
  we encode distribution a list of tuples where the 
  second element of tuple basically is probability of first element 
  in the tuple. Moreover, we define equality on distribution by 
  stating that two distributions are equal if they are permutation 
  of each other. Finally, we define a function , $uniform\_with\_replacement$, 
  to generate uniform distributions.

@@

(* Uniform distribution u*)
Definition uniform_with_replacement {A : Type} : 
  forall (l : list A), l <> [] -> dist A.
Proof.
  intros ? H.
  remember (Pos.of_nat (List.length l)) as len.
  exact (List.map 
    (fun x => (x, mk_prob 1 len)) l).
Defined.
\end{lstlisting}

We prove that the dist is a monad (\textbf{Cite some work}) by 
giving it a suitable definitions of ret and bind. Making 
it an instance of monad makes our life easier because 
we can compose a distribution $d$ $n$ times to 
returns a distribution on a vector of $n$ elements.

\begin{lstlisting}[language=Coq]
(* Probability Monad *)
Definition Ret {A : Type} (x : A) : 
  dist A := [(x, one)].

@@

Now we have all the ingredients to prove the zero-knowledge 
proof of the Schnorr protocol. We define the 
Schnorr distribution $schnorr\_distribution$
that involves the secret $x$ and 
the simulator distribution $simulator\_distribution$
that does not involve the secret $x$. 
In the Schnorr distibution we draw 
a random field element $u$ from a uniform 
distribution $uniform\_with\_replacement \text{ }lf \text{ } Hlfn$
and use this $u$ to construct a distribution; 
similarly in the simulator distribution 
we draw a random field element $u$ from 
$uniform\_with\_replacement \text{ }lf \text{ } Hlfn$
and use it construct a distribution. Using these 
two definitions, we prove that these two 
distributions are identical 
$special\_honest\_verifier\_zkp$. However, 
contrary to informal reasoning, these two 
distributions are not syntactically equal but 
semantically equal. For both distributions, 
the first component is a transcript $(a, c, r)$ and 
the second component is a rational number that represents 
its probability. The triples in both distrubtions 
are an accepting transcript (semantic) but they 
are not identical and differ syntactically; 
therefore we first apply the 
$accepting\_conversation$ to the first pair of 
both distributions which turn them into 
a boolean value (true). After this  
application both distributions are identical 
that we prove.

\begin{lstlisting}[language=Coq]
(* Distribution that involves the secret x *)
Definition schnorr_distribution  (lf : list F) 
  (Hlfn : lf <> List.nil) (x : F) (g : G) (c : F) : 
  dist sigma_proto :=
  (* draw u from a random distribution *)
  u <- (uniform_with_replacement lf Hlfn) ;;
  Ret (schnorr_protocol x g u c).

(* without secret x *)
Definition simulator_distribution (lf : list F) 
  (Hlfn : lf <> List.nil) (g h : G) (c : F) : 
  dist sigma_proto :=
  (* draw u from a random distribution *)
  u <- (uniform_with_replacement lf Hlfn) ;;
  Ret (schnorr_simulator g h u c).

Lemma special_honest_verifier_zkp : 
  forall (lf : list F) (Hlfn : lf <> List.nil) (c : F), 
  List.map (fun '(a, p) => 
    (accepting_conversation g h a, p))
    (@schnorr_distribution lf Hlfn x g c) = 
  List.map (fun '(a, p) => 
    (accepting_conversation g h a, p))
    (@simulator_distribution lf Hlfn g h c).
Proof. (* proof terms omitted *) Qed. 
  \end{lstlisting}

We shown in the function $repeat\_dist\_ntimes\_vector$.
  The reader can see from the proof 
  $uniform\_probability\_multidraw\_prob$
  that if a distribution $lf$ is repeated 
  $n$ times then the probability of this distribution 
  is $1/|lf|^n$. We use $repeat\_dist\_ntimes\_vector$ 
  when we combine multiple sigma protocols and 
  want to to prove zero-knowledge property. For example, 
  in Parallel composition when we combine $n$ sigma protocol 
  we need to need to draw a vector $n$ random numbers to 
  prove the zero-knowledge property.

\begin{lstlisting}[language=Coq]
Fixpoint repeat_dist_ntimes_vector {A : Type} 
(d : dist A) (n : nat) : dist (Vector.t A n) := 
match n with 
| 0 => Ret (@Vector.nil A)
| S n' => 
  Bind d (fun u => 
    Bind (repeat_dist_ntimes_vector d n')
    (fun v => Ret (Vector.cons _ u _ v)))
end.

Lemma uniform_probability_multidraw_prob 
{A : Type} : forall n (lf : dist A) 
(a : Vector.t A n) b (Hlf : lf <> []), 
In (a, b) (repeat_dist_ntimes_vector 
  (uniform_with_replacement lf Hlf) n) ->
b = mk_prob 1 (Pos.of_nat 
(Nat.pow (List.length lf) n)).

Definition parallel_schnorr_distribution  
  {n : nat} (lf : list F) (Hlfn : lf <> List.nil) 
  (x : F) (g : G) (cs : Vector.t F n) : 
  dist (@sigma_proto n n n) :=
  (* draw n random elements *)
  us <- repeat_dist_ntimes_vector 
    (uniform_with_replacement lf Hlfn) n ;;
  Ret (construct_parallel_schnorr x g us cs).
\end{lstlisting}

\subsection{Efficient Modular Arithmetic}
 As we stated that our formalisation is  
 abstract and can be instantiated with 
 a suitable group and field. In order 
 to run our code, we have developed 
 a formally verified Schnorr group (\textbf{cite here}). 
\begin{lstlisting}[language=Coq]
Section SchnorrGroup. 
  Context 
    {k p q : Z}
    {Hk : p = k * q + 1}
    {Hp : prime p}
    {Hq : prime q}.

  Record Schnorr_group := 
    mk_schnorr 
    {v : Z; Ha : 0 < v < p; 
    Hb : (v ^ q mod p = 1)}.

  (* Neutral Element *)
  Definition one : Schnorr_group.
    refine 
      (mk_schnorr 1 one_mod_p 
      one_pow_mod_q).
  Defined.

  Definition mul_schnorr_group 
      (u v : Schnorr_group) : Schnorr_group.
  refine(
    match u, v with 
    | mk_schnorr au Hua Hub, 
      mk_schnorr av Hva Hvb => 
      mk_schnorr (Z.modulo (au * av) p) 
      (@multiplication_bound p Hp au 
      av Hua Hva)  _
    end).
  Defined.

  (* u ^ (p - 2) is inverse of u *)
  Definition inv_schnorr_group 
  (u : Schnorr_group) : Schnorr_group.
  refine(
    match u with 
    | mk_schnorr au Hu Hv => mk_schnorr
        (Z.of_N (Npow_mod (Z.to_N au) 
        (Z.to_N (p - 2)) (Z.to_N p)))
        (@inv_schnorr_group_first au Hu)
        (inv_schnorr_group_second au Hu Hv)
    end).
  Defined.

  (* Schnorr is a commutative Group *)
  Global Instance schnorr_comm : 
    @commutative_group 
    Schnorr_group (@eq Schnorr_group) 
    mul_schnorr_group one inv_schnorr_group.
  Proof. ... Qed.

Similarly, we have encoded a prime field.

@@

(* Prime Field *)
Section ZpField.

  Context 
    {p : Z}
    {Hp : prime p}.

  Record Zp := 
    mk_zp {v : Z; Hv : Z.modulo v p = v}.

  Definition zp_inv (x : Zp) : Zp.
    refine (match x with
      | mk_zp ax Hu => mk_zp 
        (Z.modulo 
          (Z.of_N (Npow_mod (Z.to_N ax) 
          (Z.to_N (p - 2)) (Z.to_N p)))
          p) _ 
    end).
    rewrite Zmod_mod.
    exact eq_refl.
  Defined.

  Definition zp_div (x y : Zp) : Zp :=
    zp_mul x (zp_inv y).

@@

Finally, we prove that they form a vector space. 
We have encoded the scalar mulitplication of 
vector space as a pow function that takes an element from 
a Schnorr group and an element from 
a given field and returns an element in the 
Schnorr group.  The reader can see that our encoding eliminates all 
possibilities of mixing group and field, both represented 
as an integer modulo some large 
prime \cite{10.1007/978-3-662-63958-0_24}.
